Biden Predicted to Secure a Minimum 10% Lead in Popular Vote Over Trump in the 2024 Election

### 2024-03-16 outputs/paper.qmd
final;D

## Post-Stratification Data
IPUMS USA is a website that contains decennial census from 1790 to 2010, as well as survey data from the American Community Surveys (ACS) and the Puerto Rican Community Surveys from 2000 to the present [@ipumsIPUMS]. The ACS employed a monthly rolling sample of households, designed to replace the census long forms. The sampling unit was the household and encompassed all persons residing within.The annual ACS public-use samples typically include housing, demographic and economic data, as well as some other individual characteristics. For this analysis, I will use the most recent American Community Survey, the 2022 Sample, as the post-stratification data to represent the voter population. This is a weighted sample which includes persons in group quarters. This survey used cluster sampling to obtain 1-in-100 national random sample of the population. The population for this sample was the entire US population, categorized into households as subgroups, and the responses of the sampled subgroups were collected [@ipumsIPUMS].

>>>>

## Post-Stratification Data
IPUMS USA is a website that contains decennial census from 1790 to 2010, as well as survey data from the American Community Surveys (ACS) and the Puerto Rican Community Surveys from 2000 to the present [@ipumsIPUMS]. The ACS employed a monthly rolling sample of households, designed to replace the census long forms. The sampling unit was the household which includes all persons residing within. The annual ACS public-use samples typically contain housing, demographic, and economic data, as well as some other individual characteristics. For this analysis, I will use the most recent American Community Survey, the 2022 Sample, as the post-stratification data to represent the voter population. This is a weighted sample which includes persons in group quarters. This survey used cluster sampling to obtain 1-in-100 national random sample of the population. The population for this sample was the entire US population, categorized into households as subgroups, and the responses of the sampled subgroups were collected [@ipumsIPUMS].
